### 2019-07-02 response.tex

% * The preamble
% ! This TeX file uses 'amsart' for its document class. 
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
% ! 'amsmath', 'amsthm', 'amsfonts' package is automatically loaded by 'amsart' class.
% ! Below is the configuration of 'amsmath' package.
\numberwithin{equation}{section}
\allowdisplaybreaks
% ! Below is the configuration of 'amsthm' package.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollaray}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\newtheorem{iss}{Issue}
\newtheorem{rem}[thm]{Remark}
\newtheorem*{ack}{Acknowledgment}
% ! 'inputenc' package is used to specify the set of characters allowed to input into this TeX file.
% \usepackage[utf8]{inputenc}
% ! 'foutenc' package is used to specify the set of characters allowed to output into the generated pdf file.
% \usepackage[T1]{fontenc}
% ! 'amssymb', 'mathrsfs' and 'mathtools' packages provide additional math symbols from the AMS default symbol fonts. They are compatible with the AMS class and is recommended to be used.
\usepackage{amssymb}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
% ! 'hyperref' package is used to handle cross-referencing in the generated pdf file.
\usepackage[backref]{hyperref}
% ! Other packages
\usepackage{xcolor}
\usepackage{comment}
% * Top matter
\begin{document}
\title
[short title]
{Response}
\maketitle
% * Document body
We are grateful to the referees' for their helpful comments.
We have incorporated all the comments made by the referee.
Here are the specific changes in response to the comments of the referees.
\section*{Response to the comments of Referee 1}
\begin{enumerate}
\item

\end{enumerate}
% * Bibliographic references
\bibliographystyle{plain}
\bibliography{../orggtd/bib.bib}
\end{document}

### 2019-07-12 stableLimit.tex
change stableLimit.tex
change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex

%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
%---Top matter------------------------------
\begin{document}
\title
	[Superprocesses with stable branching]
	{\large Limit theorems for a class of critical superprocesses with stable branching}
		\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
%---Yan-Xia Ren
\address
	{Yan-Xia Ren\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%---Renming Song
\address
	{Renming Song\\
	Dept of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{rsong@illinois.edu}
\thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
%---Zhenyao Sun
\address
	{Zhenyao Sun\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\thanks{Zhenyao Sun is the corresponding author.}
\begin{abstract}
We consider a critical superprocess $\{X;\mathbf P_\mu\}$ with general spatial motion and spatially dependent stable branching mechanism with lowest stable index $\gamma_0 > 1$. We first show that, under some conditions, $\mathbf P_{\mu}(\|X_t\|\neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying with index $(\gamma_0-1)^{-1}$. Then we show that, for a large class of non-negative testing functions $f$, the distribution of $\{X_t(f);\mathbf P_\mu(\cdot|\|X_t\|\neq 0)\}$, after appropriate rescaling, converges weakly to a positive random variable $\mathbf z^{(\gamma_0-1)}$ with Laplace transform $E[e^{-u\mathbf z^{(\gamma_0-1)}}]=1-(1+u^{-(\gamma_0-1)})^{-1/(\gamma_0-1)}.$
\end{abstract}
\subjclass[2010]{Primary: 60J68; 60F05. Secondary 60J80; 60J25}
\keywords{Critical superprocess; stable branching, scaling limit; intrinsic ultracontractivity; regular variation}
\maketitle
\section{Introduction}

\subsection{Background}
	The study of the asymptotic behaviors of critical branching particle systems has a long history.
	It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
\begin{align}\label{eq: Kolmogorov's result with finite variance}
	n P(Z_n > 0)
	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
\end{align}
	and
\begin{align}\label{eq: Yaglom's result with finite variance}
	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
\end{align}
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see 
	\cite{Harris2002The-theory, KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results have been obtained for more general
	critical branching processes with finite 2nd moment, 
	see \cite{AsmussenHering1983Branching, AthreyaNey1974Functionals, AthreyaNey1972Branching, JoffeSpitzer1967On-multitype} for example.

@@

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
    condition. Their main result can be stated as follows.
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
	Let $M$ be the mean matrix of $\mathbf Z$. Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, 
	respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\begin{align}\label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{align}
	where $0 < \alpha \leq 1$; 
	$l$ is slowly varying at $0$;
	and the matrix $G(\mathbf s)$ is defined by
\begin{align}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{align}
    Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
	It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{align} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
    n l(a_n)
	\operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{}
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{align}
	and for each $\mathbf j \in \mathbb N_0^d$,
\begin{align}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{align}
	where $\mathbf z^{(\alpha)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}.
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.

@@

	Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to a class of critical superprocesses with general branching mechanism and general spatial motions.
	The main results of \cite{RenSongZhang2015Limit} are as follows.
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a finite measure $\mu$ on $E$.
	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition
\begin{align}\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\end{align}
	For any finite measure $\mu$ on $E$ and any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$ to denote the integral of $f$ with respect to $\mu$.
	Put $\|\mu\|=\langle 1, \mu\rangle$.
	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
\begin{align}\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(\|X_t\| \neq 0)
	\xrightarrow[t\to \infty]{} c^{-1}
\langle \phi, \mu \rangle,
\end{align}
	and for a large class of testing functions $f$ on $E$,
\begin{align}\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\end{align}
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
$\langle\cdot, \cdot \rangle_m$ denotes the inner product in $L^2(E, m)$;
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine}, we provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler version of this question has already been answered in the context of continuous-state branching processes
	(CSBPs)
	which can be viewed as superprocesses without spatial movements.
	Kyprianou and Pardo \cite{Kyprianou2008Continuous} 
	considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{align} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{align}
    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0,
\end{align}
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
	It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{align}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\end{align}
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
    Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP
	with critical branching mechanism $\psi$ satisfying Grey's condition.
	In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

	In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\begin{align}
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{align}
	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	Let $\mu$ be an arbitrary finite initial measure on $E$.
	We will show that 
	$\mathbf P_{\mu}( \| X_t\| \neq 0) $
	converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
\begin{align}
	\lim_{t\to \infty}\eta^{-1}_t \mathbf P_{\mu}( \|X_t\| \neq0)
	= \mu(\phi),
\end{align}
	and for a large class of non-negative testing functions $f$,
\begin{align}\label{eq: result2}
	\{ \eta_t X_t(f) ; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\end{align}
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ 
	$C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ 
	and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} 
	(with $\alpha=\gamma_0-1$).
	Precise statements of the assumptions and the results are presented in the next subsection.
    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $\{X; \mathbf P\}$ depends primarily on the lowest index $\gamma_0$.

\subsection{Model and results}

>>>>

% * The preamble
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{comment}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
% * Top matter
\begin{document}
\title
[Superprocesses with stable branching]
{\large Limit theorems for a class of critical superprocesses with stable branching}
\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
% ** Yan-Xia Ren
\address
{Yan-Xia Ren\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
% ** Renming Song
\address
{Renming Song\\
	Dept of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{rsong@illinois.edu}
\thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
% ** Zhenyao Sun
\address
{Zhenyao Sun\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\thanks{Zhenyao Sun is the corresponding author.}
\begin{abstract}
  We consider a critical superprocess $\{X;\mathbf P_\mu\}$ with general spatial motion and spatially dependent stable branching mechanism with lowest stable index $\gamma_0 > 1$. We first show that, under some conditions, $\mathbf P_{\mu}(\|X_t\|\neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying with index $(\gamma_0-1)^{-1}$. Then we show that, for a large class of non-negative testing functions $f$, the distribution of $\{X_t(f);\mathbf P_\mu(\cdot|\|X_t\|\neq 0)\}$, after appropriate rescaling, converges weakly to a positive random variable $\mathbf z^{(\gamma_0-1)}$ with Laplace transform $E[e^{-u\mathbf z^{(\gamma_0-1)}}]=1-(1+u^{-(\gamma_0-1)})^{-1/(\gamma_0-1)}.$
\end{abstract}
\subjclass[2010]{Primary: 60J68; 60F05. Secondary 60J80; 60J25}
\keywords{Critical superprocess; stable branching, scaling limit; intrinsic ultracontractivity; regular variation}
\maketitle
% * Main Body
% ** Introduction
\section{Introduction}
% *** Background
\subsection{Background}
The study of the asymptotic behaviors of critical branching particle systems has a long history.
It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
\begin{align}\label{eq: Kolmogorov's result with finite variance}
	n P(Z_n > 0)
	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
\begin{align}\label{eq: Yaglom's result with finite variance}
	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
For further references to these results, see \cite{Harris2002The-theory, KestenNeySpitzer1966The-Galton-Watson}.
Since then, lots of analogous results have been obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching, AthreyaNey1974Functionals, AthreyaNey1972Branching, JoffeSpitzer1967On-multitype} for example.

@@

Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
condition. Their main result can be stated as follows.
% Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
% Let $M$ be the mean matrix of $\mathbf Z$.  
Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$. 
% Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$ where $\mathbf 1$ is the vector $(1,\dots, 1)$.
Suppose that
\begin{align}
  \label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{align}
where $0 < \alpha \leq 1$; 
$l$ is slowly varying at $0$;
and the matrix $G(\mathbf s)$ is defined by
\begin{align}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{align}
Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{align} 
  \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
  n l(a_n)
	\operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{}
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{align}
and for each $\mathbf j \in \mathbb N_0^d$,
\begin{align}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{align}
where $\mathbf z^{(\alpha)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}.
For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.

@@

Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to a class of critical superprocesses with general branching mechanism and general spatial motions.
The main results of \cite{RenSongZhang2015Limit} are as follows.
Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a finite measure $\mu$ on $E$.
Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition
\begin{align}\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\end{align}
For any finite measure $\mu$ on $E$ and any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$ to denote the integral of $f$ with respect to $\mu$.
Put $\|\mu\|=\langle 1, \mu\rangle$.
Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
\begin{align}
\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(\|X_t\| \neq 0)
	\xrightarrow[t\to \infty]{} c^{-1}
  \langle \phi, \mu \rangle,
\end{align}
and for a large class of testing functions $f$ on $E$,
\begin{align}\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\end{align}
Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
$\langle\cdot, \cdot \rangle_m$ denotes the inner product in $L^2(E, m)$;
$\mathbf e$ is an exponential random variable with mean $1$;
and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
In \cite{RenSongSun2017Spine}, we provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
A simpler version of this question has already been answered in the context of continuous-state branching processes	(CSBPs) which can be viewed as superprocesses without spatial movements.
Kyprianou and Pardo \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
% He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{align} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{align}
% where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.
Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0,
\end{align}
where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{align}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
  %	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
  % \end{align}
  \xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}
\end{align}
where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.

Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP
with critical branching mechanism $\psi$ satisfying Grey's condition.
In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
